---
title: "MATES_results_analysis"
author: "Kyle Morrison"
date: "2024-01-28"
output: html_document
---
# knitr set up 
```{r setup, include = FALSE}
rm(list = ls())
# knitr setting
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE, 
  cache = TRUE,
  echo=TRUE
)
```

# Load packages
```{r}
pacman::p_load(tidyverse,
               here,
               stringr,
               purrr)
```

# Load data
```{r}
# Load data sets
dat <- read_csv(here("data", "MATES_results.csv"), skip = 0)  # 188 rows 60 columns 

task_wos1 <- read_csv(here("data", "MATES_task_WOS_1_to_1000.csv"), skip =0) # 1000 72

task_wos2 <- read_csv(here("data", "MATES_task_WOS_1001_to_2000.csv"), skip =0) # 1000 72

task_wos3 <- read_csv(here("data", "MATES_task_WOS_2001_to_3000.csv"), skip =0) # 1000 72

task_wos4 <- read_csv(here("data", "MATES_task_WOS_3001_to_3301.csv"), skip =0) # 1000 72

task_wos <- rbind(task_wos1, task_wos2, task_wos3, task_wos4)
# view(task_wos)
```

# MATES results section
Select required columns & rows for the plots 
```{r}
dat <-  select(dat, -c(StartDate, EndDate, Status, IPAddress, Progress, Duration, Finished, RecordedDate, ResponseId, RecipientLastName, RecipientFirstName, RecipientEmail, ExternalReference, LocationLatitude, LocationLongitude, DistributionChannel, UserLanguage))

dat <- dat[-c(1, 2), ]

dat

raf <- select(raf, Q1)

raf <- raf[-c(1, 2), ]

raf 

vol <- select(vol, Q1)

vol <- vol[-c(1,2), ]

vol

```

## Question 1 
What is your current stage of career?
```{r}
# Seperate rows and count total 
total_career_stage_count <- dat %>% 
  separate_rows(Q1, sep = ",\\s*") %>% 
  filter(!is.na(Q1)) %>%
  count(Q1) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_career_stage_percentage <-  total_career_stage_count %>% 
  mutate(proportion = n/sum(total_career_stage_count$n),
         percentage = proportion*100)

# Theme for all MATES plots 
MATES_theme <-  function(){ 
  theme_minimal() +
  theme(
    panel.grid.major.y = element_line(color = "gray", linetype = "dashed"),
    panel.grid.minor.y = element_blank(),
    axis.line.x = element_line(linewidth = 1.2),
    axis.line.y = element_line(linewidth = 1.2),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.text.x = element_text(hjust = 1, size = 25, color = "#666666"),
    axis.text.y = element_text(size = 20, color = "#666666"),
    legend.position = "none"
  )
  }

# Plot for survey question 1 
fig_Q1 <-  total_career_stage_count %>% 
  ggplot(aes(x = n, y =reorder(Q1, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 ,y = reorder(Q1,n)), hjust = 0.5, size = 8, color = "white") +
  geom_text(data = total_career_stage_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_career_stage_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "Question 1", size = 25)

fig_Q1

# ggsave(here("survey_results", "fig_Q1.jpg"),  width = 18, height = 10, units = "cm", scale = 2, dpi = 120)
```

## Question 2
What is your current experience with meta-analyses?
```{r}
# Seperate rows and count total 
total_ma_experience_count <- dat %>% 
  separate_rows(Q2, sep = ",\\s*") %>% 
  filter(!is.na(Q2)) %>%
  count(Q2) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_ma_experience_percentage <-  total_ma_experience_count %>% 
  mutate(proportion = n/sum(total_ma_experience_count$n),
         percentage = proportion*100)

# Plot for survey question 2 
fig_Q2 <-  total_ma_experience_count %>% 
  ggplot(aes(x = n, y =reorder(Q2, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 ,y = reorder(Q2,n)), hjust = 0.5, size = 8, color = "white") +
  geom_text(data = total_ma_experience_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_ma_experience_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "Question 2", size = 20)

fig_Q2

# ggsave(here("survey_results", "fig_Q2.jpg"),  width = 18, height = 10, units = "cm", scale = 2, dpi = 120 )
```

## Question 3 
What is your experience with systematic review or meta-analyses appraisal tools?
```{r}

# Separate rows and count total 
total_appraisal_tool_experience_count <- dat %>% 
  separate_rows(Q3, sep = ",\\s*") %>% 
  filter(!is.na(Q3)) %>%
  count(Q3) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_appraisal_tool_experience_percentage <-  total_appraisal_tool_experience_count %>% 
  mutate(proportion = n/sum(total_appraisal_tool_experience_count$n),
         percentage = proportion*100)

# Plot for survey question 3
fig_Q3 <-  total_appraisal_tool_experience_count %>% 
  ggplot(aes(x = n, y =reorder(Q3, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 ,y = reorder(Q3,n)), hjust = 0.5, size = 8, color = "white") +
  geom_text(data = total_appraisal_tool_experience_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_appraisal_tool_experience_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "Question 3", size = 15)


fig_Q3

# ggsave(here("survey_results", "fig_Q3.jpg"),  width = 18, height = 10, units = "cm", scale = 2, dpi = 120 )

```

```{r}
df_Q3 <- dat %>% 
  filter(!is.na(Q3_1_TEXT)) %>% 
  select(Q3_1_TEXT)

df_Q3

# write_csv(df_Q3, file = here("survey_results", "df_Q3.csv"))
```

## Question 4
What is the importance of reporting the software used to conduct the meta-analysis to the quality of reporting?
Referring to MATES item 1:
Do the authors report the software used to conduct the analysis within the manuscript or supplementary material?
```{r}
# Separate rows and count total 
total_software_importance_count <- dat %>% 
  filter(!is.na(Q4)) %>%
  count(Q4) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_software_importance_percentage <-  total_software_importance_count %>% 
  mutate(proportion = n/sum(total_software_importance_count$n),
         percentage = proportion*100)

# Plot for survey question 4
fig_Q4 <-  total_software_importance_count %>% 
  ggplot(aes(x = n, y =reorder(Q4, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q4,n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_software_importance_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_software_importance_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "MATES item 1", size = 15)


fig_Q4

# ggsave(here("survey_results", "fig_Q4.jpg"),  width = 18, height = 10, units = "cm", scale = 2, dpi = 120 )

```

## Question 5
Comments on MATES item 1 (e.g., potential improvements or a justification of response)
```{r}
df_Q5 <- dat %>% 
  filter(!is.na(Q5)) %>% 
  select(c(Q4,Q5))

df_Q5

# write_csv(df_Q5, file = here("survey_results", "df_Q5.csv"))

```


## Question 6
What is the importance of reporting the packages used to conduct the meta-analysis to the quality of reporting?
Referring to MATES item 2:
Do the authors report the packages used to conduct the analysis within the manuscript or supplementary material?
```{r}
# Separate rows and count total 
total_package_importance_count <- dat %>% 
  filter(!is.na(Q6)) %>%
  count(Q6) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_package_importance_percentage <-  total_package_importance_count %>% 
  mutate(proportion = n/sum(total_package_importance_count$n),
         percentage = proportion*100)

# Plot for survey question 6
fig_Q6 <-  total_package_importance_count %>% 
  ggplot(aes(x = n, y =reorder(Q6, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q6,n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_package_importance_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_package_importance_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "MATES item 2", size = 15)


fig_Q6

# ggsave(here("survey_results", "fig_Q6.jpg"),  width = 18, height = 10, units = "cm", scale = 2, dpi = 120 )

```

## Question 7
Comments on MATES item 2 (e.g., potential improvements or a justification of response)
```{r}
df_Q7 <- dat %>% 
  filter(!is.na(Q7)) %>% 
  select(c(Q6,Q7))

df_Q7

# write_csv(df_Q7, file = here("survey_results", "df_Q7.csv"))

```

## Question 8
What is the importance of reporting the version numbers of the software used to conduct the meta-analysis to the quality of reporting?
Referring to MATES item 3:
Do the authors report the version numbers of the software used within the manuscript or supplementary material?
```{r}
# Separate rows and count total 
total_version_importance_count <- dat %>% 
  filter(!is.na(Q8)) %>%
  count(Q8) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_version_importance_percentage <-  total_version_importance_count %>% 
  mutate(proportion = n/sum(total_version_importance_count$n),
         percentage = proportion*100)

# Plot for survey question 8
fig_Q8 <-  total_version_importance_count %>% 
  ggplot(aes(x = n, y =reorder(Q8, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q8,n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_version_importance_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_version_importance_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "MATES item 3", size = 15)


fig_Q8

# ggsave(here("survey_results", "fig_Q8.jpg"),  width = 18, height = 10, units = "cm", scale = 2, dpi = 120 )

```

## Question 9
Comments on MATES item 3 (e.g., potential improvements or a justification of response)
```{r}
df_Q9 <- dat %>% 
  filter(!is.na(Q9)) %>% 
  select(c(Q8,Q9))

df_Q9

# write_csv(df_Q9, file = here("survey_results", "df_Q9.csv"))

```

## Question 10
What is the importance of reporting the code used to conduct the meta-analysis to the quality of reporting?
Referring to MATES item 4:
Do the authors report the relevant code to conduct the analysis within the manuscript, supplementary material or an attached repository?
```{r}
# Seperate rows and count total 
total_code_importance_count <- dat %>% 
  filter(!is.na(Q10)) %>%
  count(Q10) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_code_importance_percentage <-  total_code_importance_count %>% 
  mutate(proportion = n/sum(total_code_importance_count$n),
         percentage = proportion*100)

# Plot for survey question 10
fig_Q10 <-  total_code_importance_count %>% 
  ggplot(aes(x = n, y =reorder(Q10, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q10,n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_code_importance_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_code_importance_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "MATES item 4", size = 15)

fig_Q10

# ggsave(here("survey_results", "fig_Q10.jpg"),  width = 18, height = 10, units = "cm", scale = 2, dpi = 120 )

```

## Question 11 
Comments on MATES item 4 (e.g., potential improvements or a justification of response)
```{r}
df_Q11 <- dat %>% 
  filter(!is.na(Q11)) %>% 
  select(c(Q10,Q11))

df_Q11

# write_csv(df_Q11, file = here("survey_results", "df_Q11.csv"))

```

## Question 12
What is the importance of reporting the primary model (or first model) used to conduct the meta-analysis to the quality of reporting?
Referring to MATES item 5:
Do the authors report the primary model (or first model) used, either as word or statistical notation within the manuscript or supplementary material?
```{r}
# Separate rows and count total 
total_model_importance_count <- dat %>% 
  filter(!is.na(Q12)) %>%
  count(Q12) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_model_importance_percentage <-  total_model_importance_count %>% 
  mutate(proportion = n/sum(total_model_importance_count$n),
         percentage = proportion*100)

# Plot for survey question 12
fig_Q12 <-  total_model_importance_count %>% 
  ggplot(aes(x = n, y =reorder(Q12, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q12,n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_model_importance_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_model_importance_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "MATES item 5", size = 15)

fig_Q12

# ggsave(here("survey_results", "fig_Q12.jpg"),  width = 18, height = 10, units = "cm", scale = 2, dpi = 120 )

```

## Question 13
Comments on MATES item 5 (e.g., potential improvements or a justification of response)
```{r}
df_Q13 <- dat %>% 
  filter(!is.na(Q13)) %>% 
  select(c(Q12,Q13))

df_Q13

# write_csv(df_Q13, file = here("survey_results", "df_Q13.csv"))

```

## Question 14 
What is the importance of reporting a justification of the primary model (or first model) used to conduct the meta-analysis to the quality of reporting?
Referring to MATES item 6:
Do the authors report a justification for the primary model (or first model) used to conduct the analysis within the manuscript or supplementary material?
```{r}
# Separate rows and count total
total_justification_importance_count <- dat %>% 
  filter(!is.na(Q14)) %>%
  count(Q14) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_justification_importance_percentage <-  total_justification_importance_count %>% 
  mutate(proportion = n/sum(total_justification_importance_count$n),
         percentage = proportion*100)

# Plot for survey question 14
fig_Q14 <-  total_justification_importance_count %>% 
  ggplot(aes(x = n, y = reorder(Q14, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q14, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_justification_importance_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_justification_importance_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "MATES item 6", size = 15)

fig_Q14

# ggsave(here("survey_results", "fig_Q14.jpg"),  width = 18, height = 10, units = "cm", scale = 2, dpi = 120 )
```

## Question 15
Comments on MATES item 6 (e.g., potential improvements or a justification of response)
```{r}
df_Q15 <- dat %>% 
  filter(!is.na(Q15)) %>% 
  select(c(Q14,Q15))

df_Q15

# write_csv(df_Q15, file = here("survey_results", "df_Q15.csv"))

```

## Question 16
What is the importance of reporting a weighting scheme for effect size estimates in a meta-analysis to the quality of reporting?
Referring to MATES item 7:
Do the authors report a weighting scheme for effect size estimates within the manuscript or supplementary material?
```{r}
# Separate rows and count total
total_weighting_scheme_importance_count <- dat %>% 
  filter(!is.na(Q16)) %>%
  count(Q16) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_weighting_scheme_importance_percentage <-  total_weighting_scheme_importance_count %>% 
  mutate(proportion = n/sum(total_weighting_scheme_importance_count$n),
         percentage = proportion*100)

# Plot for survey question 16
fig_Q16 <-  total_weighting_scheme_importance_count %>% 
  ggplot(aes(x = n, y = reorder(Q16, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q16, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_weighting_scheme_importance_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_weighting_scheme_importance_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "MATES item 7", size = 15)

fig_Q16

# ggsave(here("survey_results", "fig_Q16.jpg"),  width = 18, height = 10, units = "cm", scale = 2, dpi = 120 )
``` 

## Question 17 
Comments on MATES item 7 (e.g., potential improvements or a justification of response)
```{r}
df_Q17 <- dat %>% 
  filter(!is.na(Q17)) %>% 
  select(c(Q16,Q17))

df_Q17

# write_csv(df_Q17, file = here("survey_results", "df_Q17.csv"))

```

## Question 18
What is the importance of reporting a consideration of non-independence of effect size estimates in a meta-analysis to the quality of reporting?
Referring to MATES item 8:
Do the authors report whether there is non-independence of effect size estimates within the manuscript or supplementary material?
```{r}
# Separate rows and count total
total_non_independence_importance_count <- dat %>% 
  filter(!is.na(Q18)) %>%
  count(Q18) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_non_independence_importance_percentage <-  total_non_independence_importance_count %>% 
  mutate(proportion = n/sum(total_non_independence_importance_count$n),
         percentage = proportion*100)

# Plot for survey question 18
fig_Q18 <-  total_non_independence_importance_count %>% 
  ggplot(aes(x = n, y = reorder(Q18, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q18, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_non_independence_importance_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_non_independence_importance_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "MATES item 8", size = 15)

fig_Q18

# ggsave(here("survey_results", "fig_Q18.jpg"),  width = 18, height = 10, units = "cm", scale = 2, dpi = 120 )

```

## Question 19
Comments on MATES item 8 (e.g., potential improvements or a justification of response)
```{r}
df_Q19 <- dat %>% 
  filter(!is.na(Q19)) %>% 
  select(c(Q18,Q19))

df_Q19

# write_csv(df_Q19, file = here("survey_results", "df_Q19.csv"))

```


## Question 20
What is the importance of reporting a measure of heterogeneity between effect size estimates in a meta-analysis to the quality of reporting?
Referring to MATES item 9:
Do the authors report a measure of heterogeneity between effect size estimates within the manuscript or supplementary material?
```{r}
# Separate rows and count total for Question 20
total_heterogeneity_importance_count <- dat %>% 
  filter(!is.na(Q20)) %>%
  count(Q20) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_heterogeneity_importance_percentage <-  total_heterogeneity_importance_count %>% 
  mutate(proportion = n/sum(total_heterogeneity_importance_count$n),
         percentage = proportion*100)

# Plot for survey question 20
fig_Q20 <-  total_heterogeneity_importance_count %>% 
  ggplot(aes(x = n, y = reorder(Q20, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q20, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_heterogeneity_importance_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_heterogeneity_importance_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "MATES item 9", size = 15)

fig_Q20

# ggsave(here("survey_results", "fig_Q20.jpg"),  width = 18, height = 10, units = "cm", scale = 2, dpi = 120 )

```

## Question 21
Comments on MATES item 9 (e.g., potential improvements or a justification of response)
```{r}
df_Q21 <- dat %>% 
  filter(!is.na(Q21)) %>% 
  select(c(Q20,Q21))

df_Q21

# write_csv(df_Q21, file = here("survey_results", "df_Q21.csv"))

```

## Question 22
What is the importance of reporting the moderator variables included in a meta-regression in a meta-analysis to the quality of reporting?
Referring to MATES item 10:
Do the authors report the moderator variables included in a meta-regression within the manuscript or supplementary material?
```{r}
# Separate rows and count total for Question 22
total_moderator_variables_importance_count <- dat %>% 
  filter(!is.na(Q22)) %>%
  count(Q22) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_moderator_variables_importance_percentage <-  total_moderator_variables_importance_count %>% 
  mutate(proportion = n/sum(total_moderator_variables_importance_count$n),
         percentage = proportion*100)

# Plot for survey question 22
fig_Q22 <-  total_moderator_variables_importance_count %>% 
  ggplot(aes(x = n, y = reorder(Q22, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q22, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_moderator_variables_importance_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_moderator_variables_importance_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "MATES item 10", size = 15)

fig_Q22

# ggsave(here("survey_results", "fig_Q22.jpg"),  width = 18, height = 10, units = "cm", scale = 2, dpi = 120 )

```

## Question 23
Comments on MATES item 10 (e.g., potential improvements or a justification of response)
```{r}
df_Q23 <- dat %>% 
  filter(!is.na(Q23)) %>% 
  select(c(Q22,Q23))

df_Q23

# write_csv(df_Q23, file = here("survey_results", "df_Q23.csv"))

```


## Question 24
What is the importance of reporting a test or measure of publication bias in a meta-analysis to the quality of reporting?
Referring to MATES item 11: 
Do the authors report a test or measure of publication bias within the manuscript or supplementary material?
```{r}
# Separate rows and count total for Question 24
total_publication_bias_importance_count <- dat %>% 
  filter(!is.na(Q24)) %>%
  count(Q24) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_publication_bias_importance_percentage <-  total_publication_bias_importance_count %>% 
  mutate(proportion = n/sum(total_publication_bias_importance_count$n),
         percentage = proportion*100)

# Plot for survey question 24
fig_Q24 <-  total_publication_bias_importance_count %>% 
  ggplot(aes(x = n, y = reorder(Q24, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q24, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_publication_bias_importance_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_publication_bias_importance_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "MATES item 11", size = 15)

fig_Q24

# ggsave(here("survey_results", "fig_Q24.jpg"),  width = 18, height = 10, units = "cm", scale = 2, dpi = 120 )

```

## Question 25
Comments on MATES item 11 (e.g., potential improvements or a justification of response)
```{r}
df_Q25 <- dat %>% 
  filter(!is.na(Q25)) %>% 
  select(c(Q24,Q25))

df_Q25
# write_csv(df_Q25, file = here("survey_results", "df_Q25.csv"))

```

## Question 26
What is the importance of reporting a sensitivity analysis in a meta-analysis to the quality of reporting?
Referring to MATES items 12:
Do the authors report a sensitivity analysis in addition to a publication bias test within the manuscript or supplementary material?
```{r}
# Separate rows and count total for Question 26
total_sensitivity_analysis_importance_count <- dat %>% 
  filter(!is.na(Q26)) %>%
  count(Q26) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_sensitivity_analysis_importance_percentage <-  total_sensitivity_analysis_importance_count %>% 
  mutate(proportion = n/sum(total_sensitivity_analysis_importance_count$n),
         percentage = proportion*100)

# Plot for survey question 26
fig_Q26 <-  total_sensitivity_analysis_importance_count %>% 
  ggplot(aes(x = n, y = reorder(Q26, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q26, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_sensitivity_analysis_importance_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_sensitivity_analysis_importance_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "MATES item 12", size = 15)

fig_Q26

# ggsave(here("survey_results", "fig_Q26.jpg"),  width = 18, height = 10, units = "cm", scale = 2, dpi = 120 )

```

## Question 27
Comments on MATES item 12 (e.g., potential improvements or a justification of response)
```{r}
df_Q27 <- dat %>% 
  filter(!is.na(Q27)) %>% 
  select(c(Q26,Q27))

df_Q27

# write_csv(df_Q27, file = here("survey_results", "df_Q27.csv"))

```

## Question 28
What is the importance of reporting the total number of studies included in the meta-analysis to the quality of reporting?
Referring to MATES item 13:
Do the authors report the total number of studies within the manuscript or supplementary material?
```{r}
# Separate rows and count total for Question 28
total_studies_included_count <- dat %>% 
  filter(!is.na(Q28)) %>%
  count(Q28) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_studies_included_percentage <-  total_studies_included_count %>% 
  mutate(proportion = n/sum(total_studies_included_count$n),
         percentage = proportion*100)

# Plot for survey question 28
fig_Q28 <-  total_studies_included_count %>% 
  ggplot(aes(x = n, y = reorder(Q28, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q28, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_studies_included_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_studies_included_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "MATES item 13", size = 15)

fig_Q28

# ggsave(here("survey_results", "fig_Q28.jpg"),  width = 18, height = 10, units = "cm", scale = 2, dpi = 120 )

```

## Question 29
Comments on MATES item 13 (e.g., potential improvements or a justification of response)
```{r}
df_Q29 <- dat %>% 
  filter(!is.na(Q29)) %>% 
  select(c(Q28,Q29))

df_Q29

# write_csv(df_Q29, file = here("survey_results", "df_Q29.csv"))

```


## Question 30
What is the importance of reporting the total number of effect size estimates included in the meta-analysis to the quality of reporting?
Referring to MATES item 14:
Do the authors report the total number of effect sizes within the manuscript or supplementary material?
```{r}
# Separate rows and count total for Question 30
total_effect_size_count <- dat %>% 
  filter(!is.na(Q30)) %>%
  count(Q30) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_effect_size_percentage <-  total_effect_size_count %>% 
  mutate(proportion = n/sum(total_effect_size_count$n),
         percentage = proportion*100)

# Plot for survey question 30
fig_Q30 <-  total_effect_size_count %>% 
  ggplot(aes(x = n, y = reorder(Q30, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q30, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_effect_size_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_effect_size_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "MATES item 14", size = 15)

fig_Q30

# ggsave(here("survey_results", "fig_Q30.jpg"),  width = 18, height = 10, units = "cm", scale = 2, dpi = 120 )

```

## Question 31
Comments on MATES item 14 (e.g., potential improvements or a justification of response)
```{r}
df_Q31 <- dat %>% 
  filter(!is.na(Q31)) %>% 
  select(c(Q30,Q31))

df_Q31

# write_csv(df_Q31, file = here("survey_results", "df_Q31.csv"))

```

## Question 32
What is the importance of reporting the results using a visualisation in a meta-analysis to the quality of reporting?
Referring to MATES item 15:
Do the authors report the results using a visualisation in the manuscript or supplementary material?
```{r}
# Separate rows and count total for Question 32
total_visualisation_report_count <- dat %>% 
  filter(!is.na(Q32)) %>%
  count(Q32) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_visualisation_report_percentage <-  total_visualisation_report_count %>% 
  mutate(proportion = n/sum(total_visualisation_report_count$n),
         percentage = proportion*100)

# Plot for survey question 32
fig_Q32 <-  total_visualisation_report_count %>% 
  ggplot(aes(x = n, y = reorder(Q32, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q32, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_visualisation_report_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_visualisation_report_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "MATES item 15", size = 15)

fig_Q32

# ggsave(here("survey_results", "fig_Q32.jpg"),  width = 18, height = 10, units = "cm", scale = 2, dpi = 120 )

```

## Question 33
Comments on MATES item 15 (e.g., potential improvements or a justification of response)
```{r}
df_Q33 <- dat %>% 
  filter(!is.na(Q33)) %>% 
  select(c(Q32,Q33))

df_Q33

# write_csv(df_Q33, file = here("survey_results", "df_Q33.csv"))

```

## Question 34
What is the importance of reporting the data extracted in the meta-analysis to the quality of reporting?
Referring to MATES item 16:
Do the authors report the data extracted from each eligible primary study within the manuscript, supplementary material or external repository?
```{r}
# Separate rows and count total for Question 34
total_data_extraction_report_count <- dat %>% 
  filter(!is.na(Q34)) %>%
  count(Q34) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_data_extraction_report_percentage <-  total_data_extraction_report_count %>% 
  mutate(proportion = n/sum(total_data_extraction_report_count$n),
         percentage = proportion*100)

# Plot for survey question 34
fig_Q34 <-  total_data_extraction_report_count %>% 
  ggplot(aes(x = n, y = reorder(Q34, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q34, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_data_extraction_report_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_data_extraction_report_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "MATES item 16", size = 15)

fig_Q34

# ggsave(here("survey_results", "fig_Q34.jpg"),  width = 16, height = 10, units = "cm", scale = 2, dpi = 120 )

```

## Question 35
Comments on MATES item 16 (e.g., potential improvements or a justification of response)
```{r}
df_Q35 <- dat %>% 
  filter(!is.na(Q35)) %>% 
  select(c(Q34,Q35))

df_Q35

# write_csv(df_Q35, file = here("survey_results", "df_Q35.csv"))

```

## Question 36
What is the importance of reporting the descriptions of data created in the meta-analysis to the quality of reporting?
Referring to MATES item 17:
Do the authors report descriptions of the data extracted from each eligible within the manuscript, supplementary material or external repository?#
```{r}
# Separate rows and count total for Question 36
total_data_description_report_count <- dat %>% 
  filter(!is.na(Q36)) %>%
  count(Q36) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_data_description_report_percentage <-  total_data_description_report_count %>% 
  mutate(proportion = n/sum(total_data_description_report_count$n),
         percentage = proportion*100)

# Plot for survey question 36
fig_Q36 <-  total_data_description_report_count %>% 
  ggplot(aes(x = n, y = reorder(Q36, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q36, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_data_description_report_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_data_description_report_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "MATES item 17", size = 15)

fig_Q36

# ggsave(here("survey_results", "fig_Q36.jpg"),  width = 16, height = 10, units = "cm", scale = 2, dpi = 120 )

```

## Question 37
Comments on MATES item 17 (e.g., potential improvements or a justification of response)
```{r}
df_Q37 <- dat %>% 
  filter(!is.na(Q37)) %>% 
  select(c(Q36,Q37))

df_Q37

# write_csv(df_Q37, file = here("survey_results", "df_Q37.csv"))

```


## Question 38
Are there any elements of meta-analyses that are considered important to reporting quality that are not currently included in MATES?
```{r}
df_Q38 <- dat %>% 
  filter(!is.na(Q38)) %>% 
  select(Q38)

df_Q38

# write_csv(df_Q38, file = here("survey_results", "df_Q38.csv"))

```

## Question 39
Any final comments or feedback on MATES?
```{r}
df_Q39 <- dat %>% 
  filter(!is.na(Q39)) %>% 
  select(Q39)

df_Q39

# write_csv(df_Q39, file = here("survey_results", "df_Q39.csv"))

```

# MATES task
Filter the search string for studies that state meta-analysis or meta-regression in title.
Then take a random sample of 50 meta-analysis
```{r}
MA_task_wos <- task_wos %>% 
  filter(grepl("meta-analysis|meta-regression", `Article Title`, ignore.case = TRUE))


# write_csv(MA_task_wos, file = here("task_papers", "MATES_task_papers.csv"))

MATES_task_sample <- MA_task_wos %>%
  sample_n(50, replace = FALSE)

# write_csv(MATES_task_sample, file = here("task_papers", "MATES_task_papers_sample.csv"))

```

