---
title: "MATES_results_analysis"
author: "Kyle Morrison"
date: "latest update: `r format(Sys.time(), '%d %B %Y')`"
output:
   html_document:
    toc: true
    toc_float: true
    code_folding: show
    code_download: true
    theme: readable   # Options: cerulean, journal, flatly, readable, spacelab, united, cosmo, lumen, paper, sandstone, simplex, yeti
    highlight: kate  # Options: default, tango, pygments, kate, monochrome, espresso, zenburn, haddock, textmate
editor_options: 
  chunk_output_type: console
---
# **Set up **

## knitr set up 
```{r setup, include = FALSE}
rm(list = ls())
# knitr setting
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE, 
  cache = TRUE,
  echo=TRUE
)
```

## Load packages
```{r}
pacman::p_load(tidyverse,
               here,
               stringr,
               purrr,
               kableExtra)
```

## Load data
```{r}
# Load data sets
MATES_survey_part <- read_csv(here("data", "survey", "MATES_participant_paper_list.csv"), skip = 0) # 4757 8 

dat <- read_csv(here("data", "survey",  "MATES_survey_results.csv"), skip = 0)  # 188 rows 60 columns 

task_vol <- read_csv(here("data", "task",  "MATES_coauthor_details.csv"), skip = 0) # 30 rows 4 columns

task_pap <- read_csv(here("data", "task", "MATES_task_papers.csv"), skip = 0) # 50 rows 1 column

# MATES_task_results 

dat_task <- read_csv(here("data", "task", "MATES_task_feedback.csv"), skip = 0) # 17 rows 48 column

```

# **MATES survey **

## Extracting Survey Participants
```{r}
# Create a new column with the email address
MATES_survey_part_modified <- MATES_survey_part %>%
  mutate(Email = str_extract_all(correspondence_address, "\\b[A-Za-z0-9._%+-]+@[A-Za-z0-9.-]+\\.[A-Za-z]{2,}\\b")) %>%
  unnest(Email, keep_empty = TRUE)

MATES_survey_part_modified_distinct <- distinct(MATES_survey_part_modified, Email, .keep_all = TRUE) # select records with unique titles (removes exact duplicates)
dim(MATES_survey_part_modified_distinct) # 3969 9

# Number of rows in the data frame
total_rows <- nrow(MATES_survey_part_modified_distinct)

# Number of rows per chunk
chunk_size <- 400

# Calculate the number of chunks needed
num_chunks <- ceiling(total_rows / chunk_size)

# Loop to create each chunk
for (i in 1:num_chunks) {
  start_row <- ((i - 1) * chunk_size) + 1
  end_row <- min(i * chunk_size, total_rows)
  
  # Subset the data frame
  MATES_survey_part_modified_distinct_subset <- MATES_survey_part_modified_distinct[start_row:end_row, ]
  
  # Create the file name
  file_name <- paste("MATES_survey_participants_", start_row, "_to_", end_row, ".csv", sep = "")
  
  # Write the CSV file to the directory
  write.csv(MATES_survey_part_modified_distinct_subset, here("data", "survey", file_name))
}

  
```

Select required columns & rows for the plots 
```{r}
dat <-  select(dat, -c(StartDate, EndDate, Status, IPAddress, Progress, Duration, Finished, RecordedDate, ResponseId, RecipientLastName, RecipientFirstName, RecipientEmail, ExternalReference, LocationLatitude, LocationLongitude, DistributionChannel, UserLanguage))

dat <- dat[-c(1, 2), ]

# Table of the data
 kable(dat, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

```

## Survey Question 1 
What is your current stage of career?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total 
total_career_stage_count <- dat %>% 
  separate_rows(Q1, sep = ",\\s*") %>% 
  filter(!is.na(Q1)) %>%
  count(Q1) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_career_stage_percentage <-  total_career_stage_count %>% 
  mutate(proportion = n/sum(total_career_stage_count$n),
         percentage = proportion*100)

# Theme for all MATES plots 
MATES_theme <-  function(){ 
  theme_bw() +
  theme(
    panel.grid.major.y = element_line(color = "gray", linetype = "dashed"),
    panel.grid.minor.y = element_blank(),
    axis.line.x = element_line(linewidth = 1.2),
    axis.line.y = element_line(linewidth = 1.2),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.text.x = element_text(hjust = 1, size = 25, color = "#666666"),
    axis.text.y = element_text(size = 20, color = "#666666"),
    legend.position = "none",
    plot.caption = element_text(size = 20, face = "italic")
  )
  }

# Plot for survey question 1 
fig_Q1 <-  total_career_stage_count %>% 
  ggplot(aes(x = n, y =reorder(Q1, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 ,y = reorder(Q1,n)), hjust = 0.5, size = 8, color = "white") +
  geom_text(data = total_career_stage_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_career_stage_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "Survey Question 1\nThe value in each bar is the total number of participants")

fig_Q1

# ggsave(here("survey_results", "fig_Q1.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120)

```

## Survey Question 2
What is your current experience with meta-analyses?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total 
total_ma_experience_count <- dat %>% 
  separate_rows(Q2, sep = ",\\s*") %>% 
  filter(!is.na(Q2)) %>%
  count(Q2) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_ma_experience_percentage <-  total_ma_experience_count %>% 
  mutate(proportion = n/sum(total_ma_experience_count$n),
         percentage = proportion*100)

# Plot for survey question 2 
fig_Q2 <-  total_ma_experience_count %>% 
  ggplot(aes(x = n, y =reorder(Q2, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 ,y = reorder(Q2,n)), hjust = 0.5, size = 8, color = "white") +
  geom_text(data = total_ma_experience_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_ma_experience_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "Survey Question 2\nThe value in each bar is the total number of participants")

fig_Q2

# ggsave(here("survey_results", "fig_Q2.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120 )

```

## Question 3 
What is your experience with systematic review or meta-analyses appraisal tools?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total 
total_appraisal_tool_experience_count <- dat %>% 
  separate_rows(Q3, sep = ",\\s*") %>% 
  filter(!is.na(Q3)) %>%
  count(Q3) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_appraisal_tool_experience_percentage <-  total_appraisal_tool_experience_count %>% 
  mutate(proportion = n/sum(total_appraisal_tool_experience_count$n),
         percentage = proportion*100)

# Plot for survey question 3
fig_Q3 <-  total_appraisal_tool_experience_count %>% 
  ggplot(aes(x = n, y =reorder(Q3, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 ,y = reorder(Q3,n)), hjust = 0.5, size = 8, color = "white") +
  geom_text(data = total_appraisal_tool_experience_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_appraisal_tool_experience_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "Survey Question 3\nThe value in each bar is the total number of participants")


fig_Q3

# ggsave(here("survey_results", "fig_Q3.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120 )

```

```{r}
# Filter dataframe for question 3
df_Q3 <- dat %>% 
  filter(!is.na(Q3_1_TEXT)) %>% 
  select(Q3_1_TEXT)

# Table for question 3
 kable(df_Q3, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")
 
# write_csv(df_Q3, file = here("survey_results", "df_Q3.csv"))

```

## Question 4
What is the importance of reporting the software used to conduct the meta-analysis to the quality of reporting?

Referring to MATES item 1:

Do the authors report the software used to conduct the analysis within the manuscript or supplementary material?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total 
total_software_importance_count <- dat %>% 
  filter(!is.na(Q4)) %>%
  count(Q4) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_software_importance_percentage <-  total_software_importance_count %>% 
  mutate(proportion = n/sum(total_software_importance_count$n),
         percentage = proportion*100)

# Plot for survey question 4
fig_Q4 <-  total_software_importance_count %>% 
  ggplot(aes(x = n, y =reorder(Q4, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q4,n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_software_importance_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_software_importance_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 1\nThe value in each bar is the total number of participants")


fig_Q4

# ggsave(here("survey_results", "fig_Q4.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120 )

```

## Question 5
Comments on MATES item 1 (e.g., potential improvements or a justification of response)
```{r}
# Filter dataframe for question 5
df_Q5 <- dat %>% 
  filter(!is.na(Q5)) %>% 
  select(c(Q4,Q5))

# Table for question 5
 kable(df_Q5, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(df_Q5, file = here("survey_results", "df_Q5.csv"))

```

## Question 6
What is the importance of reporting the packages used to conduct the meta-analysis to the quality of reporting?

Referring to MATES item 2:

Do the authors report the packages used to conduct the analysis within the manuscript or supplementary material?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total 
total_package_importance_count <- dat %>% 
  filter(!is.na(Q6)) %>%
  count(Q6) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_package_importance_percentage <-  total_package_importance_count %>% 
  mutate(proportion = n/sum(total_package_importance_count$n),
         percentage = proportion*100)

# Plot for survey question 6
fig_Q6 <-  total_package_importance_count %>% 
  ggplot(aes(x = n, y =reorder(Q6, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q6,n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_package_importance_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_package_importance_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 2\nThe value in each bar is the total number of participants")


fig_Q6

# ggsave(here("survey_results", "fig_Q6.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120 )

```

## Question 7
Comments on MATES item 2 (e.g., potential improvements or a justification of response)
```{r}
# Filter for question 7
df_Q7 <- dat %>% 
  filter(!is.na(Q7)) %>% 
  select(c(Q6,Q7))

# Table for question 7
 kable(df_Q7, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(df_Q7, file = here("survey_results", "df_Q7.csv"))
 
```

## Question 8
What is the importance of reporting the version numbers of the software used to conduct the meta-analysis to the quality of reporting?

Referring to MATES item 3:

Do the authors report the version numbers of the software used within the manuscript or supplementary material?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total 
total_version_importance_count <- dat %>% 
  filter(!is.na(Q8)) %>%
  count(Q8) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_version_importance_percentage <-  total_version_importance_count %>% 
  mutate(proportion = n/sum(total_version_importance_count$n),
         percentage = proportion*100)

# Plot for survey question 8
fig_Q8 <-  total_version_importance_count %>% 
  ggplot(aes(x = n, y =reorder(Q8, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q8,n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_version_importance_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_version_importance_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 3\nThe value in each bar is the total number of participants")


fig_Q8

# ggsave(here("survey_results", "fig_Q8.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120 )

```

## Question 9
Comments on MATES item 3 (e.g., potential improvements or a justification of response)
```{r}
# Filter for question 9
df_Q9 <- dat %>% 
  filter(!is.na(Q9)) %>% 
  select(c(Q8,Q9))

# Table for question 9
 kable(df_Q9, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(df_Q9, file = here("survey_results", "df_Q9.csv"))

```

## Question 10
What is the importance of reporting the code used to conduct the meta-analysis to the quality of reporting?

Referring to MATES item 4:

Do the authors report the relevant code to conduct the analysis within the manuscript, supplementary material or an attached repository?
```{r,fig.width=16, fig.height=8}
# Seperate rows and count total 
total_code_importance_count <- dat %>% 
  filter(!is.na(Q10)) %>%
  count(Q10) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_code_importance_percentage <-  total_code_importance_count %>% 
  mutate(proportion = n/sum(total_code_importance_count$n),
         percentage = proportion*100)

# Plot for survey question 10
fig_Q10 <-  total_code_importance_count %>% 
  ggplot(aes(x = n, y =reorder(Q10, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q10,n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_code_importance_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_code_importance_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 4\nThe value in each bar is the total number of participants")

fig_Q10

# ggsave(here("survey_results", "fig_Q10.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120 )

```

## Question 11 
Comments on MATES item 4 (e.g., potential improvements or a justification of response)
```{r}
# Filter for question 11
df_Q11 <- dat %>% 
  filter(!is.na(Q11)) %>% 
  select(c(Q10,Q11))

# Table for question 11
 kable(df_Q11, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(df_Q11, file = here("survey_results", "df_Q11.csv"))
 
```

## Question 12
What is the importance of reporting the primary model (or first model) used to conduct the meta-analysis to the quality of reporting?

Referring to MATES item 5:

Do the authors report the primary model (or first model) used, either as word or statistical notation within the manuscript or supplementary material?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total 
total_model_importance_count <- dat %>% 
  filter(!is.na(Q12)) %>%
  count(Q12) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_model_importance_percentage <-  total_model_importance_count %>% 
  mutate(proportion = n/sum(total_model_importance_count$n),
         percentage = proportion*100)

# Plot for survey question 12
fig_Q12 <-  total_model_importance_count %>% 
  ggplot(aes(x = n, y =reorder(Q12, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q12,n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_model_importance_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_model_importance_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 5\nThe value in each bar is the total number of participants")

fig_Q12

# ggsave(here("survey_results", "fig_Q12.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120 )

```

## Question 13
Comments on MATES item 5 (e.g., potential improvements or a justification of response)
```{r}
# Filter for question 13
df_Q13 <- dat %>% 
  filter(!is.na(Q13)) %>% 
  select(c(Q12,Q13))

# Table for question 13
 kable(df_Q13, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(df_Q13, file = here("survey_results", "df_Q13.csv"))

```

## Question 14 
What is the importance of reporting a justification of the primary model (or first model) used to conduct the meta-analysis to the quality of reporting?

Referring to MATES item 6:

Do the authors report a justification for the primary model (or first model) used to conduct the analysis within the manuscript or supplementary material?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total
total_justification_importance_count <- dat %>% 
  filter(!is.na(Q14)) %>%
  count(Q14) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_justification_importance_percentage <-  total_justification_importance_count %>% 
  mutate(proportion = n/sum(total_justification_importance_count$n),
         percentage = proportion*100)

# Plot for survey question 14
fig_Q14 <-  total_justification_importance_count %>% 
  ggplot(aes(x = n, y = reorder(Q14, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q14, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_justification_importance_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_justification_importance_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 6\nThe value in each bar is the total number of participants")

fig_Q14

# ggsave(here("survey_results", "fig_Q14.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120 )

```

## Question 15
Comments on MATES item 6 (e.g., potential improvements or a justification of response)
```{r}
# Filter for question 15
df_Q15 <- dat %>% 
  filter(!is.na(Q15)) %>% 
  select(c(Q14,Q15))

# Table for question 15
 kable(df_Q15, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(df_Q15, file = here("survey_results", "df_Q15.csv"))

```

## Question 16
What is the importance of reporting a weighting scheme for effect size estimates in a meta-analysis to the quality of reporting?

Referring to MATES item 7:

Do the authors report a weighting scheme for effect size estimates within the manuscript or supplementary material?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total
total_weighting_scheme_importance_count <- dat %>% 
  filter(!is.na(Q16)) %>%
  count(Q16) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_weighting_scheme_importance_percentage <-  total_weighting_scheme_importance_count %>% 
  mutate(proportion = n/sum(total_weighting_scheme_importance_count$n),
         percentage = proportion*100)

# Plot for survey question 16
fig_Q16 <-  total_weighting_scheme_importance_count %>% 
  ggplot(aes(x = n, y = reorder(Q16, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q16, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_weighting_scheme_importance_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_weighting_scheme_importance_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 7\nThe value in each bar is the total number of participants")

fig_Q16

# ggsave(here("survey_results", "fig_Q16.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120 )
``` 

## Question 17 
Comments on MATES item 7 (e.g., potential improvements or a justification of response)
```{r}
# Filter for question 17
df_Q17 <- dat %>% 
  filter(!is.na(Q17)) %>% 
  select(c(Q16,Q17))

# Table for question 17
 kable(df_Q17, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "250%", height = "800px")

# write_csv(df_Q17, file = here("survey_results", "df_Q17.csv"))

```

## Question 18
What is the importance of reporting a consideration of non-independence of effect size estimates in a meta-analysis to the quality of reporting?

Referring to MATES item 8:

Do the authors report whether there is non-independence of effect size estimates within the manuscript or supplementary material?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total
total_non_independence_importance_count <- dat %>% 
  filter(!is.na(Q18)) %>%
  count(Q18) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_non_independence_importance_percentage <-  total_non_independence_importance_count %>% 
  mutate(proportion = n/sum(total_non_independence_importance_count$n),
         percentage = proportion*100)

# Plot for survey question 18
fig_Q18 <-  total_non_independence_importance_count %>% 
  ggplot(aes(x = n, y = reorder(Q18, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q18, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_non_independence_importance_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_non_independence_importance_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 8\nThe value in each bar is the total number of participants")

fig_Q18

# ggsave(here("survey_results", "fig_Q18.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120 )

```

## Question 19
Comments on MATES item 8 (e.g., potential improvements or a justification of response)
```{r}
# Filter for question 19
df_Q19 <- dat %>% 
  filter(!is.na(Q19)) %>% 
  select(c(Q18,Q19))

# Table for question 19
 kable(df_Q19, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")
 
# write_csv(df_Q19, file = here("survey_results", "df_Q19.csv"))

```


## Question 20
What is the importance of reporting a measure of heterogeneity between effect size estimates in a meta-analysis to the quality of reporting?

Referring to MATES item 9:

Do the authors report a measure of heterogeneity between effect size estimates within the manuscript or supplementary material?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total for Question 20
total_heterogeneity_importance_count <- dat %>% 
  filter(!is.na(Q20)) %>%
  count(Q20) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_heterogeneity_importance_percentage <-  total_heterogeneity_importance_count %>% 
  mutate(proportion = n/sum(total_heterogeneity_importance_count$n),
         percentage = proportion*100)

# Plot for survey question 20
fig_Q20 <-  total_heterogeneity_importance_count %>% 
  ggplot(aes(x = n, y = reorder(Q20, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q20, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_heterogeneity_importance_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_heterogeneity_importance_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 9\nThe value in each bar is the total number of participants")

fig_Q20

# ggsave(here("survey_results", "fig_Q20.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120 )

```

## Question 21
Comments on MATES item 9 (e.g., potential improvements or a justification of response)
```{r}
# Filter for question 21
df_Q21 <- dat %>% 
  filter(!is.na(Q21)) %>% 
  select(c(Q20,Q21))

# Table for question 21
 kable(df_Q21, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")
 
# write_csv(df_Q21, file = here("survey_results", "df_Q21.csv"))

```

## Question 22
What is the importance of reporting the moderator variables included in a meta-regression in a meta-analysis to the quality of reporting?

Referring to MATES item 10:

Do the authors report the moderator variables included in a meta-regression within the manuscript or supplementary material?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total for Question 22
total_moderator_variables_importance_count <- dat %>% 
  filter(!is.na(Q22)) %>%
  count(Q22) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_moderator_variables_importance_percentage <-  total_moderator_variables_importance_count %>% 
  mutate(proportion = n/sum(total_moderator_variables_importance_count$n),
         percentage = proportion*100)

# Plot for survey question 22
fig_Q22 <-  total_moderator_variables_importance_count %>% 
  ggplot(aes(x = n, y = reorder(Q22, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q22, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_moderator_variables_importance_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_moderator_variables_importance_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 10\nThe value in each bar is the total number of participants")

fig_Q22

# ggsave(here("survey_results", "fig_Q22.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120 )

```

## Question 23
Comments on MATES item 10 (e.g., potential improvements or a justification of response)
```{r}
# Filter for question 23
df_Q23 <- dat %>% 
  filter(!is.na(Q23)) %>% 
  select(c(Q22,Q23))

# Table for question 23
 kable(df_Q23, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(df_Q23, file = here("survey_results", "df_Q23.csv"))

```

## Question 24
What is the importance of reporting a test or measure of publication bias in a meta-analysis to the quality of reporting?

Referring to MATES item 11: 

Do the authors report a test or measure of publication bias within the manuscript or supplementary material?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total for Question 24
total_publication_bias_importance_count <- dat %>% 
  filter(!is.na(Q24)) %>%
  count(Q24) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_publication_bias_importance_percentage <-  total_publication_bias_importance_count %>% 
  mutate(proportion = n/sum(total_publication_bias_importance_count$n),
         percentage = proportion*100)

# Plot for survey question 24
fig_Q24 <-  total_publication_bias_importance_count %>% 
  ggplot(aes(x = n, y = reorder(Q24, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q24, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_publication_bias_importance_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_publication_bias_importance_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 11\nThe value in each bar is the total number of participants")

fig_Q24

# ggsave(here("survey_results", "fig_Q24.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120 )

```

## Question 25
Comments on MATES item 11 (e.g., potential improvements or a justification of response)
```{r}
# Filter for question 25
df_Q25 <- dat %>% 
  filter(!is.na(Q25)) %>% 
  select(c(Q24,Q25))

# Table for question 25
 kable(df_Q25, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(df_Q25, file = here("survey_results", "df_Q25.csv"))

```

## Question 26
What is the importance of reporting a sensitivity analysis in a meta-analysis to the quality of reporting?

Referring to MATES items 12:

Do the authors report a sensitivity analysis in addition to a publication bias test within the manuscript or supplementary material?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total for Question 26
total_sensitivity_analysis_importance_count <- dat %>% 
  filter(!is.na(Q26)) %>%
  count(Q26) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_sensitivity_analysis_importance_percentage <-  total_sensitivity_analysis_importance_count %>% 
  mutate(proportion = n/sum(total_sensitivity_analysis_importance_count$n),
         percentage = proportion*100)

# Plot for survey question 26
fig_Q26 <-  total_sensitivity_analysis_importance_count %>% 
  ggplot(aes(x = n, y = reorder(Q26, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q26, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_sensitivity_analysis_importance_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_sensitivity_analysis_importance_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 12\nThe value in each bar is the total number of participants")

fig_Q26

# ggsave(here("survey_results", "fig_Q26.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120 )

```

## Question 27
Comments on MATES item 12 (e.g., potential improvements or a justification of response)
```{r}
# Filter for question 27
df_Q27 <- dat %>% 
  filter(!is.na(Q27)) %>% 
  select(c(Q26,Q27))

# Table for question 27
 kable(df_Q27, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(df_Q27, file = here("survey_results", "df_Q27.csv"))
 
```

## Question 28
What is the importance of reporting the total number of studies included in the meta-analysis to the quality of reporting?

Referring to MATES item 13:

Do the authors report the total number of studies within the manuscript or supplementary material?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total for Question 28
total_studies_included_count <- dat %>% 
  filter(!is.na(Q28)) %>%
  count(Q28) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_studies_included_percentage <-  total_studies_included_count %>% 
  mutate(proportion = n/sum(total_studies_included_count$n),
         percentage = proportion*100)

# Plot for survey question 28
fig_Q28 <-  total_studies_included_count %>% 
  ggplot(aes(x = n, y = reorder(Q28, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q28, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_studies_included_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_studies_included_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 13\nThe value in each bar is the total number of participants")

fig_Q28

# ggsave(here("survey_results", "fig_Q28.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120 )

```

## Question 29
Comments on MATES item 13 (e.g., potential improvements or a justification of response)
```{r}
# Filter for question 29
df_Q29 <- dat %>% 
  filter(!is.na(Q29)) %>% 
  select(c(Q28,Q29))

# Table for question 29
 kable(df_Q29, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(df_Q29, file = here("survey_results", "df_Q29.csv"))

```

## Question 30
What is the importance of reporting the total number of effect size estimates included in the meta-analysis to the quality of reporting?

Referring to MATES item 14:

Do the authors report the total number of effect sizes within the manuscript or supplementary material?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total for Question 30
total_effect_size_count <- dat %>% 
  filter(!is.na(Q30)) %>%
  count(Q30) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_effect_size_percentage <-  total_effect_size_count %>% 
  mutate(proportion = n/sum(total_effect_size_count$n),
         percentage = proportion*100)

# Plot for survey question 30
fig_Q30 <-  total_effect_size_count %>% 
  ggplot(aes(x = n, y = reorder(Q30, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q30, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_effect_size_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_effect_size_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 14\nThe value in each bar is the total number of participants")

fig_Q30

# ggsave(here("survey_results", "fig_Q30.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120 )

```

## Question 31
Comments on MATES item 14 (e.g., potential improvements or a justification of response)
```{r}
# Filter for question 31
df_Q31 <- dat %>% 
  filter(!is.na(Q31)) %>% 
  select(c(Q30,Q31))

# Table for question 31
 kable(df_Q31, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(df_Q31, file = here("survey_results", "df_Q31.csv"))

```

## Question 32
What is the importance of reporting the results using a visualisation in a meta-analysis to the quality of reporting?

Referring to MATES item 15:

Do the authors report the results using a visualisation in the manuscript or supplementary material?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total for Question 32
total_visualisation_report_count <- dat %>% 
  filter(!is.na(Q32)) %>%
  count(Q32) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_visualisation_report_percentage <-  total_visualisation_report_count %>% 
  mutate(proportion = n/sum(total_visualisation_report_count$n),
         percentage = proportion*100)

# Plot for survey question 32
fig_Q32 <-  total_visualisation_report_count %>% 
  ggplot(aes(x = n, y = reorder(Q32, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q32, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_visualisation_report_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_visualisation_report_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 15\nThe value in each bar is the total number of participants")

fig_Q32

# ggsave(here("survey_results", "fig_Q32.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120 )

```

## Question 33
Comments on MATES item 15 (e.g., potential improvements or a justification of response)
```{r}
# Filter for question 33
df_Q33 <- dat %>% 
  filter(!is.na(Q33)) %>% 
  select(c(Q32,Q33))

# Table for question 33
 kable(df_Q33, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(df_Q33, file = here("survey_results", "df_Q33.csv"))

```

## Question 34
What is the importance of reporting the data extracted in the meta-analysis to the quality of reporting?

Referring to MATES item 16:

Do the authors report the data extracted from each eligible primary study within the manuscript, supplementary material or external repository?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total for Question 34
total_data_extraction_report_count <- dat %>% 
  filter(!is.na(Q34)) %>%
  count(Q34) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_data_extraction_report_percentage <-  total_data_extraction_report_count %>% 
  mutate(proportion = n/sum(total_data_extraction_report_count$n),
         percentage = proportion*100)

# Plot for survey question 34
fig_Q34 <-  total_data_extraction_report_count %>% 
  ggplot(aes(x = n, y = reorder(Q34, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q34, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_data_extraction_report_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_data_extraction_report_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 16\nThe value in each bar is the total number of participants")

fig_Q34

# ggsave(here("survey_results", "fig_Q34.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120 )

```

## Question 35
Comments on MATES item 16 (e.g., potential improvements or a justification of response)
```{r}
# Filter for question 35
df_Q35 <- dat %>% 
  filter(!is.na(Q35)) %>% 
  select(c(Q34,Q35))

# Table for question 35
 kable(df_Q35, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(df_Q35, file = here("survey_results", "df_Q35.csv"))

```

## Question 36
What is the importance of reporting the descriptions of data created in the meta-analysis to the quality of reporting?

Referring to MATES item 17:

Do the authors report descriptions of the data extracted from each eligible within the manuscript, supplementary material or external repository?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total for Question 36
total_data_description_report_count <- dat %>% 
  filter(!is.na(Q36)) %>%
  count(Q36) %>% 
  arrange(desc(n))

# Calculate count as a percentage
total_data_description_report_percentage <-  total_data_description_report_count %>% 
  mutate(proportion = n/sum(total_data_description_report_count$n),
         percentage = proportion*100)

# Plot for survey question 36
fig_Q36 <-  total_data_description_report_count %>% 
  ggplot(aes(x = n, y = reorder(Q36, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q36, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = total_data_description_report_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(total_data_description_report_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 17\nThe value in each bar is the total number of participants")

fig_Q36

# ggsave(here("survey_results", "fig_Q36.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120 )

```

## Question 37
Comments on MATES item 17 (e.g., potential improvements or a justification of response)
```{r}
# Filter for question 37
df_Q37 <- dat %>% 
  filter(!is.na(Q37)) %>% 
  select(c(Q36,Q37))

# Table for question 37
 kable(df_Q37, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(df_Q37, file = here("survey_results", "df_Q37.csv"))


```

## Question 38
Are there any elements of meta-analyses that are considered important to reporting quality that are not currently included in MATES?
```{r}
# Filter for question 38
df_Q38 <- dat %>% 
  filter(!is.na(Q38)) %>% 
  select(Q38)

# Table fpr question 38
 kable(df_Q38, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(df_Q38, file = here("survey_results", "df_Q38.csv"))

```

## Question 39
Any final comments or feedback on MATES?
```{r}
# Filter for question 39
df_Q39 <- dat %>% 
  filter(!is.na(Q39)) %>% 
  select(Q39)

# Table for question 39
 kable(df_Q39, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(df_Q39, file = here("survey_results", "df_Q39.csv"))

```

# **MATES task**

## Task study allocation
```{r}
# Set seed for reproducibility
set.seed(42)

# Combine the expanded papers with the repeated author names
task_pap_assigned <- task_pap %>%
  slice(rep(1:n(), each = 4)) %>%
  mutate(Name = rep(task_vol$Name, length.out = n())) %>%
  left_join(task_vol %>% 
  select(Name, Email), by = "Name") %>%
  arrange(Name)

# write.csv(task_pap_assigned, file.path(here("data", "task"),"MATES_task_pap_assigned.csv"))

```

## MATES task feedback

Select required columns & rows for the feedback plots 
```{r}
dat_task <-  select(dat_task, -c(StartDate, EndDate, Status, IPAddress, Progress, Duration, Finished, RecordedDate, ResponseId, RecipientLastName, RecipientFirstName, RecipientEmail, ExternalReference, LocationLatitude, LocationLongitude, DistributionChannel, UserLanguage))

dat_task <- dat_task[-c(1, 2), ]

```

## Question 2
Provide feedback and suggest rewording of the following item (if necessary):

Referring to MATES item 1:

**MATES item 1: Software reporting**

Question

o	Do the authors report the software or programming language used to conduct the analysis (i.e., the software or programming language used to conduct the computations, statistical models, and inferences comprising the meta-analysis) in the manuscript or supplementary material?

Criteria for ‘Yes’

o	The authors have reported the software or programming language used to conduct the analysis in the manuscript or supplementary material.

Criteria for ‘No’

o	The authors have not reported the software or programming language used to conduct the analysis in the manuscript or supplementary material.

Criteria for ‘Not Applicable’

o	There is no ‘Not Applicable’ option for MATES item 1.

```{r}
# Filter for task question 2
dat_task_Q2 <- dat_task %>% 
  select(c(Q3, Q2))

# Table for task question 2
 kable(dat_task_Q2, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(dat_task_Q2, file = here("task_results", "dat_task_Q2.csv"))

```

## Question 3
How difficult was MATES item 1: Software reporting to implement?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total for Task Question 5 (Software Reporting Difficulty)
software_difficulty_count <- dat_task %>% 
  filter(!is.na(Q3)) %>%
  count(Q3) %>% 
  arrange(desc(n))

# Calculate count as a percentage
software_difficulty_percentage <-  software_difficulty_count %>% 
  mutate(proportion = n/sum(software_difficulty_count$n),
         percentage = proportion*100)

# Plot for survey question 36
fig_task_Q3 <-  software_difficulty_count %>% 
  ggplot(aes(x = n, y = reorder(Q3, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q3, n)), hjust = 0.5, size = 8, color = "white") +
 geom_text(data = software_difficulty_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(software_difficulty_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 1\nThe value in each bar is the total number of participants")

fig_task_Q3

# ggsave(here("task_results", "fig_task_Q3.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120 )

```

## Question 4
Provide feedback and suggest rewording of the following item (if necessary):

Referring to MATES item 2:

**MATES item 2: Code reporting**

Question 

o	Do the authors report any relevant code used to conduct the analysis (i.e., the code used to conduct the computations, statistical models, and inferences comprising the meta-analysis) in the manuscript, supplementary material, or external repository? 

Criteria for ‘Yes’

o	The authors have reported any relevant code used to conduct the analysis in the manuscript, supplementary material, or external repository.

Criteria for ‘No’

o	The authors have not reported any relevant code used to conduct the analysis in the manuscript, supplementary material, or external repository.

Criteria for ‘Not Applicable’

o	The authors have used a GUI/click based software that does not produce a code or syntax. Alternatively, the authors have not reported the software used to conduct the analysis (i.e., ‘No’ to MATES item 1).

```{r}
# Filter for task question 4
dat_task_Q4 <- dat_task %>% 
  select(c(Q5,Q4))

# Table for task question 4
 kable(dat_task_Q4, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(dat_task_Q4, file = here("task_results", "dat_task_Q4.csv"))

```

## Question 5 
How difficult was MATES item 2: Code reporting to implement?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total for Task Question 5 (Code Reporting Difficulty)
code_difficulty_count <- dat_task %>% 
  filter(!is.na(Q5)) %>%
  count(Q5) %>% 
  arrange(desc(n))

# Calculate count as a percentage
code_difficulty_percentage <-  code_difficulty_count %>% 
  mutate(proportion = n/sum(code_difficulty_count$n),
         percentage = proportion*100)

# Plot for survey question 5
fig_task_Q5 <-  code_difficulty_count %>% 
  ggplot(aes(x = n, y = reorder(Q5, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q5, n)), hjust = 0.5, size = 8, color = "white") +
  geom_text(data = code_difficulty_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(code_difficulty_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 2\nThe value in each bar is the total number of participants")

fig_task_Q5

# ggsave(here("task_results", "fig_task_Q5.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120)

```

## Question 6
Provide feedback and suggest rewording of the following item (if necessary):

Referring to MATES item 3:

**MATES item 3: Number of included primary studies reporting**

Question 

o	Do the authors report the total number of primary studies (i.e., separate individual articles) included in the meta-analysis in the manuscript or supplementary material? 

Criteria for ‘Yes’

o	The authors have reported the total number of primary studies synthesised in the meta-analysis in the manuscript or supplementary material. The total number of studies can be inferred from a screening flowchart (e.g., PRISMA flowchart), or the authors can state the number of studies per subgroup analysis. 

Criteria for ‘No’

o	The authors have not reported the total number of primary studies synthesised in the meta-analysis in the manuscript or supplementary material. The total number of studies cannot be inferred by counting from a forest plot, or from a provided dataset. 

Criteria for ‘Not Applicable’

o	There is no ‘Not Applicable’ option for MATES item 3.

```{r}
# Filter for task question 6
dat_task_Q6 <- dat_task %>% 
  select(c(Q7,Q6))

# Table for table question 6
 kable(dat_task_Q6, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(dat_task_Q6, file = here("task_results", "dat_task_Q6.csv"))

```

## Question 7
How difficult was MATES item 3: Number of included primary studies reporting to implement?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total for Task Question 6 (Number of Included Studies Reporting Difficulty)
study_difficulty_count <- dat_task %>% 
  filter(!is.na(Q7)) %>%
  count(Q7) %>% 
  arrange(desc(n))

# Calculate count as a percentage
study_difficulty_percentage <- study_difficulty_count %>% 
  mutate(proportion = n/sum(study_difficulty_count$n),
         percentage = proportion*100)

# Plot for survey question 7
fig_task_Q7 <- study_difficulty_count %>% 
  ggplot(aes(x = n, y = reorder(Q7, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q7, n)), hjust = 0.5, size = 8, color = "white") +
  geom_text(data = study_difficulty_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(study_difficulty_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 3\nThe value in each bar is the total number of participants")

fig_task_Q7

# ggsave(here("task_results", "fig_task_Q7.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120)

```

## Question 8
Provide feedback and suggest rewording of the following item (if necessary):

Referring to MATES item 4:

**MATES item 4: Number of included effect sizes reporting**

Question 

o	Do the authors report the total number of effect size estimates synthesised in the meta-analysis in the manuscript or supplementary material? 

Criteria for ‘Yes’

o	The authors have reported the total number of effect sizes estimates synthesised in the meta-analysis in the manuscript or supplementary material. The total number of effect sizes cannot be inferred by counting and must be stated explicitly.

Criteria for ‘No’

o	The authors have not reported the total number of effect sizes synthesised in the meta-analysis in the manuscript or supplementary material. The total number of effect sizes cannot be inferred by counting and must be stated explicitly.

Criteria for ‘Not Applicable’

o	There is no ‘Not Applicable’ option for MATES item 4.

```{r}
# Filter for task question 8
dat_task_Q8 <- dat_task %>% 
  select(c(Q9,Q8))

# Table for task question 6
 kable(dat_task_Q6, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(dat_task_Q8, file = here("task_results", "dat_task_Q8.csv"))

```

## Question 9
How difficult was MATES item 4: Number of included effect size reporting to implement?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total for Task Question 6 (Number of Included Studies Reporting Difficulty)
effectsize_difficulty_count <- dat_task %>% 
  filter(!is.na(Q9)) %>%
  count(Q9) %>% 
  arrange(desc(n))

# Calculate count as a percentage
effectsize_difficulty_percentage <- effectsize_difficulty_count %>% 
  mutate(proportion = n/sum(effectsize_difficulty_count$n),
         percentage = proportion*100)

# Plot for survey question 6
fig_task_Q9 <- effectsize_difficulty_count %>% 
  ggplot(aes(x = n, y = reorder(Q9, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q9, n)), hjust = 0.5, size = 8, color = "white") +
  geom_text(data = effectsize_difficulty_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(effectsize_difficulty_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 4\nThe value in each bar is the total number of participants")

fig_task_Q9

# ggsave(here("survey_results", "fig_task_Q9.jpg"),  width = 16, height = 10, units = "cm", scale = 2, dpi = 120)

```

## Question 10
Provide feedback and suggest rewording of the following item (if necessary):

Referring to MATES item 5:

**MATES item 5: Effect size statistic formula reporting**

Question 

o	Do the authors report the formula (or reference for formula) for the effect size statistic/measure used (e.g., Zr, Hedge’s g, Cohen’s d, or lnRR) in the manuscript or supplementary material?

Criteria for ‘Yes’

o	The authors have reported the formula (or reference for formula) for the effect size statistic/measure used in the manuscript or supplementary material.

Criteria for ‘No’

o	The authors have not reported the formula (or reference for formula) for the effect size statistic/measure used in the manuscript or supplementary material.

Criteria for ‘Not Applicable’

o	There is no ‘Not Applicable’ option for MATES item 5.

```{r}
# Filter for task question 10
dat_task_Q10 <- dat_task %>% 
  select(c(Q11,Q10))

# Table for task question 10
 kable(dat_task_Q10, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(dat_task_Q10, file = here("task_results", "dat_task_Q10.csv"))

```

## Question 11
How difficult was MATES item 5: Effect size statistic/measure reporting to implement?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total for Task Question 11 (Effect Size Statistic/Measure Reporting Difficulty)
effectsize_formula_difficulty_count <- dat_task %>% 
  filter(!is.na(Q11)) %>%
  count(Q11) %>% 
  arrange(desc(n))

# Calculate count as a percentage
effectsize_formula_difficulty_percentage <- effectsize_formula_difficulty_count %>% 
  mutate(proportion = n/sum(effectsize_formula_difficulty_count$n),
         percentage = proportion*100)

# Plot for survey question 11
fig_task_Q11 <- effectsize_formula_difficulty_count %>% 
  ggplot(aes(x = n, y = reorder(Q11, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q11, n)), hjust = 0.5, size = 8, color = "white") +
  geom_text(data = effectsize_formula_difficulty_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(effectsize_formula_difficulty_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 4\nThe value in each bar is the total number of participants")

fig_task_Q11

# ggsave(here("task_results", "fig_task_Q11.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120)

```

## Question 12
Provide feedback and suggest rewording of the following item (if necessary):

Referring to MATES item 6:

**MATES item 6: Model type reporting**

Question 

o	Do the authors report the type of the meta-analytic/meta-regression model (e.g., fixed, random, or multi-level models), either descriptively or in statistical notation in the manuscript or supplementary material? 

Criteria for ‘Yes’

o	The authors have reported the type of the meta-analytic/meta-regression model, either descriptively or in statistical notation in the manuscript or supplementary material.

Criteria for ‘No’

o	The authors have not reported the type of the meta-analytic/meta-regression model, either descriptively or in statistical notation in the manuscript or supplementary material.

Criteria for ‘Not Applicable’

o	There is no ‘Not Applicable’ option for MATES item 6.

```{r}
# Filter for task question 12
dat_task_Q12 <- dat_task %>% 
  select(c(Q13,Q12))

# Table for task question 12
 kable(dat_task_Q12, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(dat_task_Q12, file = here("task_results", "dat_task_Q12.csv"))

```

## Question 13
How difficult was MATES item 6: Model type reporting to implement?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total for Task Question 13 (Model Type Reporting Difficulty)
model_type_difficulty_count <- dat_task %>% 
  filter(!is.na(Q13)) %>%
  count(Q13) %>% 
  arrange(desc(n))

# Calculate count as a percentage
model_type_difficulty_percentage <- model_type_difficulty_count %>% 
  mutate(proportion = n/sum(model_type_difficulty_count$n),
         percentage = proportion*100)

# Plot for survey question 13
fig_task_Q13 <- model_type_difficulty_count %>% 
  ggplot(aes(x = n, y = reorder(Q13, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q13, n)), hjust = 0.5, size = 8, color = "white") +
  geom_text(data = model_type_difficulty_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(model_type_difficulty_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 6\nThe value in each bar is the total number of participants")

fig_task_Q13

# ggsave(here("task_results", "fig_task_Q13.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120)

```

## Question 14
Provide feedback and suggest rewording of the following item (if necessary):

Referring to MATES item 7:

**MATES item 7: Effect size weights reporting**

Question 

o	Do the authors report the sampling variance, sampling error or equivalent (i.e., strategy to assign weights) of effect size estimates in the manuscript or supplementary material? 	

Criteria for ‘Yes’

o	The authors have reported the sampling variance, sampling error or equivalent of effect size estimates in the manuscript or supplementary material. 

Criteria for ‘No’

o	The authors have not reported the sampling variance, sampling error or equivalent of effect size estimates in the manuscript or supplementary material.

Criteria for ‘Not Applicable’

o	The authors have conducted a meta-analysis without weights (i.e., unweighted meta-analysis).

```{r}
# Filter for task question 14
dat_task_Q14 <- dat_task %>% 
  select(c(Q15,Q14))

# Table for task question 14
 kable(dat_task_Q14, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(dat_task_Q14, file = here("task_results", "dat_task_Q14.csv"))

```

## Question 15
How difficult was MATES item 7: Effect size weights reporting to implement?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total for Task Question 15 (Effect Size Weights Reporting Difficulty)
effect_size_weights_difficulty_count <- dat_task %>% 
  filter(!is.na(Q15)) %>%
  count(Q15) %>% 
  arrange(desc(n))

# Calculate count as a percentage
effect_size_weights_difficulty_percentage <- effect_size_weights_difficulty_count %>% 
  mutate(proportion = n/sum(effect_size_weights_difficulty_count$n),
         percentage = proportion*100)

# Plot for survey question 15
fig_task_Q15 <- effect_size_weights_difficulty_count %>% 
  ggplot(aes(x = n, y = reorder(Q15, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q15, n)), hjust = 0.5, size = 8, color = "white") +
  geom_text(data = effect_size_weights_difficulty_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(effect_size_weights_difficulty_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 7\nThe value in each bar is the total number of participants")

fig_task_Q15

# ggsave(here("task_results", "fig_task_Q15.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120)

```

## Question 16
Provide feedback and suggest rewording of the following item (if necessary):

Referring to MATES item 8:

**MATES item 8: Effect size dependence (non-independence) reporting**

Question 

o	Do the authors report the dependence (e.g., multiplicity or, repeated measure) of effect size estimates (e.g., acknowledge multiple effect sizes were taken from a single study) in the manuscript or supplementary material?

Criteria for ‘Yes’

o	The authors have reported whether there is dependence of effect size estimates in the manuscript or supplementary material. If a meta-analysis reports that effect size estimates are independent allocate ‘Yes’.

Criteria for ‘No’

o	The authors have not reported whether there is dependence of effect size estimates in the manuscript or supplementary material.

Criteria for ‘Not Applicable’

o	There is no ‘Not Applicable’ option for MATES item 8.

```{r}
# Filter for task question 16
dat_task_Q16 <- dat_task %>% 
  select(c(Q17,Q16))

# Table for task question 16
 kable(dat_task_Q16, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(dat_task_Q16, file = here("task_results", "dat_task_Q16.csv"))

```

## Question 17
How difficult was MATES item 8: Effect size dependence (non-independence) reporting to implement?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total for Task Question 17 (Effect Size Dependence Reporting Difficulty)
effect_size_dependence_difficulty_count <- dat_task %>% 
  filter(!is.na(Q17)) %>%
  count(Q17) %>% 
  arrange(desc(n))

# Calculate count as a percentage
effect_size_dependence_difficulty_percentage <- effect_size_dependence_difficulty_count %>% 
  mutate(proportion = n/sum(effect_size_dependence_difficulty_count$n),
         percentage = proportion*100)

# Plot for survey question 17
fig_task_Q17 <- effect_size_dependence_difficulty_count %>% 
  ggplot(aes(x = n, y = reorder(Q17, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q17, n)), hjust = 0.5, size = 8, color = "white") +
  geom_text(data = effect_size_dependence_difficulty_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(effect_size_dependence_difficulty_count$n*1.3))) +
  MATES_theme() +
  labs(caption = "MATES item 8\nThe value in each bar is the total number of participants")

fig_task_Q17

# ggsave(here("task_results", "fig_task_Q17.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120)

```

## Question 18

Provide feedback and suggest rewording of the following item (if necessary):

Referring to MATES item 9:

**MATES item 9: Overall mean effect reporting**

Question 

o	Do the authors report the overall mean effect of the meta-analyses/meta-regression using a plot, table or within text in the manuscript or supplementary material?

Criteria for ‘Yes’

o	The authors reported the overall mean effect of the meta-analyses/meta-regression in the text, or within a plot or table in the manuscript or supplementary material.

Criteria for ‘No’

o	The authors have not reported the overall mean effect of the meta-analyses/meta-regression in the text, or within a plot or table in the manuscript or supplementary material.

Criteria for ‘Not Applicable’

o	There is no ‘Not Applicable’ option for MATES item 9.

```{r}
# Filter for task question 18
dat_task_Q18 <- dat_task %>% 
  select(c(Q19,Q18))

# Table for task question 18
 kable(dat_task_Q18, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(dat_task_Q18, file = here("task_results", "dat_task_Q18.csv"))

```

## Question 19 
How difficult was MATES item 9: Overall mean effect reporting to implement?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total for Task Question 19 (Overall Mean Effect Reporting Difficulty)
mean_effect_difficulty_count <- dat_task %>% 
  filter(!is.na(Q19)) %>%
  count(Q19) %>% 
  arrange(desc(n))

# Calculate count as a percentage
mean_effect_difficulty_percentage <- mean_effect_difficulty_count %>% 
  mutate(proportion = n/sum(mean_effect_difficulty_count$n),
         percentage = proportion*100)

# Plot for survey question 19
fig_task_Q19 <- mean_effect_difficulty_count %>% 
  ggplot(aes(x = n, y = reorder(Q19, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q19, n)), hjust = 0.5, size = 8, color = "white") +
  geom_text(data = mean_effect_difficulty_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(mean_effect_difficulty_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "MATES item 9: Overall Mean Effect Reporting", size = 15)

fig_task_Q19

# ggsave(here("task_results", "fig_task_Q19.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120)

```

## Question 20

Provide feedback and suggest rewording of the following item (if necessary):

Referring to MATES item 10:

**MATES item 10: Heterogeneity reporting**

Question 

o	Do the authors report an assessment of heterogeneity (e.g., I2, tau2, 𝜎 2 or, Q-statistic) between effect size estimates in the manuscript or supplementary material?

Criteria for ‘Yes’

o	The authors have reported an assessment of heterogeneity between effect size estimates in the manuscript or supplementary material. 	

Criteria for ‘No’

o	The authors have not reported an assessment of heterogeneity between effect size estimates in the manuscript or supplementary material. 	

Criteria for ‘Not Applicable’

o	The study has stated that the analysis is unweighted. 

```{r}
# Filter for task question 20
dat_task_Q20 <- dat_task %>% 
  select(c(Q21,Q20))

# Table for task question 20
 kable(dat_task_Q20, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(dat_task_Q20, file = here("task_results", "dat_task_Q20.csv"))

```

## Question 21
"How difficult was MATES item 10: Heterogeneity reporting to implement?"
```{r,fig.width=16, fig.height=8}
# Separate rows and count total for Task Question 21 (Heterogeneity Reporting Difficulty)
heterogeneity_difficulty_count <- dat_task %>% 
  filter(!is.na(Q21)) %>%
  count(Q21) %>% 
  arrange(desc(n))

# Calculate count as a percentage
heterogeneity_difficulty_percentage <- heterogeneity_difficulty_count %>% 
  mutate(proportion = n/sum(heterogeneity_difficulty_count$n),
         percentage = proportion*100)

# Plot for survey question 21
fig_task_Q21 <- heterogeneity_difficulty_count %>% 
  ggplot(aes(x = n, y = reorder(Q21, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q21, n)), hjust = 0.5, size = 8, color = "white") +
  geom_text(data = heterogeneity_difficulty_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(heterogeneity_difficulty_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "MATES item 10: Heterogeneity Reporting", size = 15)

fig_task_Q21

# ggsave(here("task_results", "fig_task_Q21.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120)

```

## Question 22
Provide feedback and suggest rewording of the following item (if necessary):

Referring to MATES item 11:

**MATES item 11: Publication bias reporting**

Question 

o	Do the authors report an assessment of publication bias in the manuscript or supplementary material?

Criteria for ‘Yes’

o	The authors have reported an assessment of publication bias in the manuscript or supplementary material.

Criteria for ‘No’

o	The authors have not reported an assessment of publication bias in the manuscript or supplementary material.

Criteria for ‘Not Applicable’

o	The authors report that an assessment of publication bias cannot be conducted.

```{r}
# Filter for task question 22
dat_task_Q22 <- dat_task %>% 
  select(c(Q23,Q22))

# Table for task question 22
 kable(dat_task_Q22, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(dat_task_Q22, file = here("task_results", "dat_task_Q22.csv"))

```

## Question 23
How difficult was MATES item 11: Publication bias reporting to implement?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total for Task Question 23 (Publication Bias Reporting Difficulty)
publication_bias_difficulty_count <- dat_task %>% 
  filter(!is.na(Q23)) %>%
  count(Q23) %>% 
  arrange(desc(n))

# Calculate count as a percentage
publication_bias_difficulty_percentage <- publication_bias_difficulty_count %>% 
  mutate(proportion = n/sum(publication_bias_difficulty_count$n),
         percentage = proportion*100)

# Plot for survey question 23
fig_task_Q23 <- publication_bias_difficulty_count %>% 
  ggplot(aes(x = n, y = reorder(Q23, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q23, n)), hjust = 0.5, size = 8, color = "white") +
  geom_text(data = publication_bias_difficulty_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(publication_bias_difficulty_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "MATES item 11: Publication Bias Reporting", size = 15)

fig_task_Q23

# ggsave(here("task_results", "fig_task_Q23.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120)

```

## Question 24

Provide feedback and suggest rewording of the following item (if necessary):

Referring to MATES item 12:

**MATES item 12: Sensitivity analysis reporting**

Question 

o	Do the authors report a sensitivity analysis or subset analysis in addition to the publication bias assessment (e.g., leave-one-out analysis, use of alternative model or within-study risk of bias assessment) in the manuscript or supplementary material?   

Criteria for ‘Yes’

o	The authors reported a sensitivity analysis in addition to the publication bias assessment in the manuscript or supplementary material.  

Criteria for ‘No’

o	The authors have not reported a sensitivity analysis in addition to the publication bias assessment   in the manuscript or supplementary material. 

Criteria for ‘Not Applicable’

o	There is no ‘Not Applicable’ option for MATES item 12.

```{r}
# Filter for task question 24
dat_task_Q24 <- dat_task %>% 
  select(c(Q25,Q24))

# Table for task question 24
 kable(dat_task_Q24, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(dat_task_Q24, file = here("task_results", "dat_task_Q24.csv"))

```

## Question 25
How difficult was MATES item 12: Sensitivity analysis reporting to implement?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total for Task Question 25 (Sensitivity Analysis Reporting Difficulty)
sensitivity_analysis_difficulty_count <- dat_task %>% 
  filter(!is.na(Q25)) %>%
  count(Q25) %>% 
  arrange(desc(n))

# Calculate count as a percentage
sensitivity_analysis_difficulty_percentage <- sensitivity_analysis_difficulty_count %>% 
  mutate(proportion = n/sum(sensitivity_analysis_difficulty_count$n),
         percentage = proportion*100)

# Plot for survey question 25
fig_task_Q25 <- sensitivity_analysis_difficulty_count %>% 
  ggplot(aes(x = n, y = reorder(Q25, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q25, n)), hjust = 0.5, size = 8, color = "white") +
  geom_text(data = sensitivity_analysis_difficulty_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(sensitivity_analysis_difficulty_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "MATES item 12: Sensitivity Analysis Reporting", size = 15)

fig_task_Q25

# ggsave(here("task_results", "fig_task_Q25.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120)

```

## Question 26

Provide feedback and suggest rewording of the following item (if necessary):

Referring to MATES item 13:

**MATES item 13: Data reporting/archiving**

Question 

o	Do the authors report the data (i.e., used to calculate effect sizes and conduct the meta-analysis) extracted from each eligible primary study (i.e., research paper) in the manuscript, supplementary material, or external repository?

Criteria for ‘Yes’

o	The authors have reported the data extracted from each eligible primary in the manuscript, supplementary material, or external repository. In cases when the authors state the data is sensitive and cannot be shared allocate ‘Yes’. 

Criteria for ‘No’

o	The authors have not reported the data extracted from each eligible primary study the manuscript, supplementary material, or external repository.

Criteria for ‘Not Applicable’

o	There is no ‘Not Applicable’ option for MATES item 13.


```{r}
# Filter for task question 26
dat_task_Q26 <- dat_task %>% 
  select(c(Q27,Q26))

# Table for task question 26
 kable(dat_task_Q26, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(dat_task_Q26, file = here("task_results", "dat_task_Q26.csv"))

```

## Question 27
How difficult was MATES item 13: Data reporting/archiving to implement?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total for Task Question 27 (Data Reporting/Archiving Difficulty)
data_archiving_difficulty_count <- dat_task %>% 
  filter(!is.na(Q27)) %>%
  count(Q27) %>% 
  arrange(desc(n))

# Calculate count as a percentage
data_archiving_difficulty_percentage <- data_archiving_difficulty_count %>% 
  mutate(proportion = n/sum(data_archiving_difficulty_count$n),
         percentage = proportion*100)

# Plot for survey question 27
fig_task_Q27 <- data_archiving_difficulty_count %>% 
  ggplot(aes(x = n, y = reorder(Q27, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q27, n)), hjust = 0.5, size = 8, color = "white") +
  geom_text(data = data_archiving_difficulty_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(data_archiving_difficulty_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "MATES item 13: Data Reporting/Archiving", size = 15)

fig_task_Q27

# ggsave(here("task_results", "fig_task_Q27.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120)

```

## Question 28
Provide feedback and suggest rewording of the following item (if necessary):

Referring to MATES item 14:

**MATES item 14: Variable description reporting/archiving**

Question 

o	Do the authors report descriptions of the variables extracted (i.e., meta-data or columns in dataset) from each eligible study primary study (i.e., research paper) in the manuscript, supplementary material, or external repository?

Criteria for ‘Yes’

o	The authors have reported descriptions of the variables extracted from each eligible study primary study in the manuscript, supplementary material, or external repository.

Criteria for ‘No’

o	The authors have not reported descriptions of the variables extracted from each eligible study primary study in the manuscript, supplementary material, or external repository.

Criteria for ‘Not Applicable’

o	The authors have not reported the data extracted from each eligible primary study in the manuscript, supplementary material, or external repository (i.e., ‘No’ for MATES item 13) or the authors have reported that the data cannot be provided because the data is sensitive.

```{r}
# Filter for task question 28
dat_task_Q28 <- dat_task %>% 
  select(c(Q29,Q28))

# Table for task question 28
 kable(dat_task_Q28, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(dat_task_Q28, file = here("task_results", "dat_task_Q28.csv"))

```

## Question 29
How difficult was MATES item 14: Variable description reporting to implement?
```{r,fig.width=16, fig.height=8}
# Separate rows and count total for Task Question 29 (Variable Description Reporting Difficulty)
variable_description_difficulty_count <- dat_task %>% 
  filter(!is.na(Q29)) %>%
  count(Q29) %>% 
  arrange(desc(n))

# Calculate count as a percentage
variable_description_difficulty_percentage <- variable_description_difficulty_count %>% 
  mutate(proportion = n/sum(variable_description_difficulty_count$n),
         percentage = proportion*100)

# Plot for survey question 29
fig_task_Q29 <- variable_description_difficulty_count %>% 
  ggplot(aes(x = n, y = reorder(Q29, n)), hjust = 0.5) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, x = n/2 , y = reorder(Q29, n)), hjust = 0.5, size = 8, color = "white") +
  geom_text(data = variable_description_difficulty_percentage, aes(label = paste0("(", round(percentage, 1), "%)"), x = n), 
            hjust = -0.1, size = 8, color = "black", fontface = "bold") +
  scale_fill_identity(guide = "none") +
  scale_x_continuous(expand = c(0,0), limits = c(0, max(variable_description_difficulty_count$n*1.3))) +
  MATES_theme() +
  labs(tag = "MATES item 14: Variable Description Reporting", size = 15)

fig_task_Q29

# ggsave(here("task_results", "fig_task_Q29.jpg"),  width = 16, height = 8, units = "cm", scale = 2, dpi = 120)

```

## Question 30
Provide overall comments on MATES (e.g. order of questions, structure of questions or on glossary of terms)
```{r}
# Filter for task question 30
dat_task_Q30 <- dat_task %>% 
  select(Q30)

# Table for task question 30
 kable(dat_task_Q30, "html") %>%
    kable_styling("bordered", position = "left") %>%
    scroll_box(width = "150%", height = "400px")

# write_csv(dat_task_Q30, file = here("task_results", "dat_task_Q30.csv"))

```
